\documentclass[10pt,a4paper,twoside]{mins}

\usepackage{enumitem}
\usepackage{booktabs}



\setcommittee{BEMOSS Research Project}
\setshortcommittee{Committee Short}
\setmembers{
	\role{Dr. Miah}{},
    \role{Brian Lauer}{}
}

\setdate{\today, 3:00 pm}

\apologies{} %If no-one gives apologies, leave blank and will be dropped
\absent{} %If no-one is absent, leave blank, and it will be dropped
\alsopresent{} %If no-one is a visitor, leave blank and it will be dropped

\setisAgenda{}%leave as blank for regular minutes. Set to True if agenda.

\begin{document}
\begin{minutes}
\begin{center}\emph{Meeting Opened at [3:31pm]}\end{center}
\begin{business}
\item Bob and I met for around 20 minutes to discuss 

\item  Scholarship discussion



\item Grant proposal

Research grant proposal under BEMOSS May 3
\item Github repository
All documentation will be maintained in a github repository.
Create Github account and send username to Dr. Miah. A Google Drive with the same name as the Github repository will be created. 
It is named docsBemoss. 

\item
Talk to Mr. Mattus about getting a laptop for research. It must be installed with Ubuntu administrative privileges. 

Send him an email:

Hello Mr. Mattus, I will be working on a project with Dr. Miah. For that we would like to request a laptop available in the department if possible so that we can install Ubuntu operating system. 

Try to go see him in the afternoon.
\item Learn Github Bash terminal commands:

Git add
Git commit -m adding files
Git remote add origin 'url'

Go through Github tutorials.

\item Upload latex file to Drive

\end{business};
\begin{center}\emph{Meeting Closed at [4:32pm]}\end{center}
\end{minutes}
\nextmeeting{[Some Date], [Some Time], [Some Place]}
\newpage
\begin{minutes}
    \begin{business}
        \item Email Mr. Mattus again on Monday, May 6.
        \item Need to get a laptop 
        
    \end{business}
\end{minutes}





\end{document}

